Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-09-26 doc/JFLA2022/paper.tex
changes in the concrete example (end of Section 2)

\TODO[Pierre]{
  Using the equations of $H'$ as rewrite rules, we studied the
  number of steps  of the battle starting with the hydra of Figure~\ref{fig:start} and $0$ as initial step. This number has
at least $2^{10^{21}}$ binary digits. Obtaining this result is an interesting example of relationship between proof and computation.}

>>>>

Using $H'$ equations as rewrite rules, we can study a concrete example of hydra battle. Let us start with the hydra of figure~\ref{fig:start} and $0$ as initial step.
By a combination of rewriting and induction, we prove that the number of steps of the considered battle has at least $2^{10^{21}}$ binary digits.
